\LARGE Performance Evaluation of Xenomai 3

### 2015-10-20 paper.tex
Add : config table
\table tag doesn't seems to work properly (not visible when added)
still can't reference table using \ref tag (line 153)

% TODO : add config table

@@

\bibliographystyle{plain}
\begin{thebibliography}{9}%use this if you have <=9 bib refs
	\bibitem {rtai}{\it https://www.rtai.org/}
	\bibitem {sel4}{\it http://ssrg.nicta.com.au/projects/seL4/}
	\bibitem {debian}{\it http://debian.beagleboard.org/images/bone-debian-7.5-2014-05-14-2gb.img.xz}
	\bibitem {kernel}{\it https://github.com/beagleboard/linux}
\end{thebibliography}

>>>>

\begin{tabular}{|l| p{3cm} |l|}
\hline
Kernel & Patches & source\\ \hline
mainline   & none & n/a \\ \hline
PREEMPT\_RT & patch-3.14.39-rt37 & \cite{p-rt} \\ \hline
Xenomai 2  & ipipe-core-3.14.39-arm-9 + xenomai v2.6.4 (2015-07-13 HEAD) & \cite{p-ipipe} \cite{git-x2.6} \\ \hline
Xenomai 3  & ipipe-core-3.14.39-arm-9 + xenomai v3.0  & \cite{p-ipipe} \cite{git-x3} \\ \hline
\end{tabular}

@@

\bibliographystyle{plain}
\begin{thebibliography}{9}%use this if you have <=9 bib refs
	\bibitem {rtai}{\it https://www.rtai.org/}
	\bibitem {sel4}{\it http://ssrg.nicta.com.au/projects/seL4/}
	\bibitem {debian}{\it http://debian.beagleboard.org/images/bone-debian-7.5-2014-05-14-2gb.img.xz}
	\bibitem {kernel}{\it https://github.com/beagleboard/linux}
	\bibitem {p-rt}{\it https://www.kernel.org/pub/linux/kernel/projects/rt/3.14/}
	\bibitem {p-ipipe}{\it http://download.gna.org/adeos/patches/v3.x/arm/ipipe-core-3.14.39-arm-9.patch}
	\bibitem {git-x2.6}{\it http://git.xenomai.org/xenomai-2.6.git/}
	\bibitem {git-x3}{\it http://git.xenomai.org/xenomai-3.git/}
\end{thebibliography}
